---
title: "GroupA_HW4"
author: "A. Gottardi, Edoardo XYZ, Alessandro UVW, L.F. Palacios Flores"
output: 
  html_document:
    toc: true
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if(!require(ellipse)) install.packages("ellipse")
library(ellipse)
if(!require(ggcorrplot)) install.packages("ggcorrplot")
library(ggcorrplot)
if(!require(PerformanceAnalytics)) install.packages("PerformanceAnalytics")
library(PerformanceAnalytics)
if(!require(skimr)) install.packages("skimr")
library(skimr)
if(!require(corrplot)) install.packages("corrplot")
library(corrplot)
library(ggplot2)
```

# "Doubt the data until the data leave no room for doubt." - Henri Poincaré


Load the data and see print descriptive statistics

```{r}
train_df <- read.csv("train.csv")

head(train_df)
skim(train_df)
summary(train_df)
```

* id:	Unique ID for the customer
* Gender:	Gender of the customer
* Age:	Age of the customer
* Driving_License:	0 for Customer does not have DL, 1 for Customer already has DL
* Region_Code:	Unique code for the region of the customer
* Previously_Insured:	1 : Customer already has Vehicle Insurance, 0 : Customer doesn't have Vehicle Insurance. PROBABLY NEEDS TO BE REMOVED. A customer is probably going to renew his insurance contract.
* Vehicle_Age:	Age of the Vehicle
* Vehicle_Damage:	1 : Customer got his/her vehicle damaged in the past. 0 : Customer didn't get his/her vehicle damaged in the past.
* Annual_Premium:	The amount customer needs to pay as premium in the year
* Policy_Sales_Channel:	Anonymized Code for the channel of outreaching to the customer ie. Different Agents, Over Mail, Over Phone, In Person, etc.
* Vintage:	Number of Days, Customer has been associated with the company
* Response:	1 : Customer is interested, 0 : Customer is not interested

Transform the data into a proper data types to work with them. 

```{r}
data <- read.csv("train.csv", stringsAsFactors = T)
columns_to_convert <- c("Driving_License", "Region_Code", "Previously_Insured", "Policy_Sales_Channel", "Response")
data[columns_to_convert] <- lapply(data[columns_to_convert], as.factor)
```

Plot the distribution of the categorical variables

```{r}
factor_columns <- sapply(data, is.factor)
factor_variable_names <- names(factor_columns[factor_columns])
par(mfrow = c(1, length(factor_variable_names)))  # Set up a multi-panel plot
for (col in factor_variable_names) {
  barplot(table(data[[col]]), main = col, xlab = col, ylab = "Frequency")
}
```

Plot the distribution of the numerical variables

```{r}
numeric_columns <- sapply(data, is.numeric)
numeric_variable_names <- names(numeric_columns[numeric_columns])
par(mfrow = c(1, length(numeric_variable_names)))  # Set up a multi-panel plot
for (col in numeric_variable_names) {
  hist(data[[col]], main = col, xlab = col, ylab = "Frequency")
}
```

Plot the correlation of the numerical variables

```{r}
corrplot(
  cor(data[, numeric_columns]),  # Calculate correlation matrix, remove missing values
  method = "color",  # Specify method for plotting correlations (using colors)
  type = "upper",    # Specify type of correlation plot (upper triangular)
  order = "hclust",  # Specify order of rows and columns (hierarchical clustering)
  tl.col = "black",  # Set color of text labels (axis labels) to black
  tl.srt = 90,       # Set rotation angle for text labels (orthogonal to the axis)
  addCoef.col = "black",  # Set color of correlation coefficients to black
  tl.cex = 1,      # Set text label character expansion (font size)
  number.cex = 1  # Set text label character expansion for correlation values
)
```

Compute independence test of categorical variables using the Pearson's Chi-Squared test.

```{r, warning=FALSE}
# Dataframe to store values
chi_squared_results <- data.frame(
  Variable1 = c(),
  Variable2 = c(),
  p_value = c()
)

k <- 2
for (i in factor_variable_names[1:7]){
  for (j in factor_variable_names[k:8]){
    # Extract the variables for the chi-squared test
    var1 <- data[, i]
    var2 <- data[, j]
    
    # Create a contingency table
    contingency_table <- table(var1, var2)
    
    # Perform the chi-squared test
    result <- chisq.test(contingency_table)

    # Add new row
    new_row <- data.frame(
      Variable1 = i,
      Variable2 = j,
      p_value = result$p.value
    )    
    # Store the result in the list
    chi_squared_results <- rbind(chi_squared_results, new_row)
  }
  k <- k + 1
}
# Print the results
# print(chi_squared_results)
max_row <- chi_squared_results[which.max(chi_squared_results[['p_value']]), ]
print(max_row)
```